---
title: "Homework 6"
author: "RuiJun Chen"
date: "11/25/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(gridExtra)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

```{r}
birth_data = read_csv('./data/birthweight.csv') %>% janitor::clean_names()

#look for missing data
colSums(is.na(birth_data))

birth_data = 
  birth_data %>% 
  mutate(
    babysex = as.factor(if_else(babysex == 1, "male", "female")),
    frace = case_when(
      (frace == 1) ~ "white",
      (frace == 2) ~ "black",
      (frace == 3) ~ "asian",
      (frace == 4) ~ "puerto_rican",
      (frace == 8) ~ "other",
      (frace == 9) ~ "unknown",
    ),
    frace = as.factor(frace),
    mrace = case_when(
      (mrace == 1) ~ "white",
      (mrace == 2) ~ "black",
      (mrace == 3) ~ "asian",
      (mrace == 4) ~ "puerto_rican",
      (mrace == 8) ~ "other",
      (mrace == 9) ~ "unknown",
    ),
    mrace = as.factor(mrace),
    malform = as.factor(if_else(malform == 0, "absent", "present"))
  )
```
There is no missing data in any of the columns. The variables babysex, frace, mrace, and malform were successfully converted into factor variables.

Exploring the data by plotting everything:
```{r}
par(mfrow = c(4, 5))

vars = birth_data %>% select(-bwt) %>% colnames()
plots = list()
for (i in 1:length(vars)) {
  plots[[i]] = ggplot(birth_data, aes_string(x = vars[i], y = "bwt")) + geom_point()
}
do.call(grid.arrange, plots)
```

From the scatter plots, seems that bhead, blength, delwt, gaweeks, malform, momage, and wtgain appear most correlated with birth weight, which we add to our hypothesis model
```{r}
hypothesis_model = 
  lm(bwt ~ bhead + blength + delwt + gaweeks + malform + momage + wtgain, 
     data = birth_data)
all_model = lm(bwt ~ ., data = birth_data)
hypothesis_model %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 4)
all_model %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 4)

birth_data %>% 
  add_predictions(hypothesis_model) %>% 
  add_residuals(hypothesis_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

```{r}
length_age_model = lm(bwt ~ blength + gaweeks, data = birth_data)
interaction_model = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex +
                         blength * babysex + bhead * blength * babysex, data = birth_data)

cv_df = 
  crossv_mc(birth_data, 100) #%>% 
  #mutate(
  #  train = map(train, as_tibble),
  #  test = map(test, as_tibble)
  #)

cv_df =
  cv_df %>% 
  mutate(
    hypothesis_model = map(train, ~lm(bwt ~ bhead + blength + delwt + gaweeks + malform + 
                                        momage + wtgain, data = .x)), 
    #all_model = map(train, ~lm(bwt ~ ., data = .x)),
    length_age_model = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction_model = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + 
                                         bhead * babysex + blength * babysex + 
                                         bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_hypothesis_model = map2_dbl(hypothesis_model, test, ~rmse(model = .x, data = .y)),
    #rmse_all_model = map2_dbl(all_model, test, ~rmse(model = .x, data = .y)),
    rmse_length_age_model = map2_dbl(length_age_model, test, ~rmse(model = .x, data = .y)),
    rmse_interaction_model = map2_dbl(interaction_model, test, ~rmse(model = .x, data = .y)),
    )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
simple_model = lm(tmax ~ tmin, data = weather_df)
simple_model %>% broom::glance() %>% select(r.squared) %>% pull(1)
temp = simple_model %>% broom::tidy() %>% select(estimate) %>% pull(1)
log(temp[1] * temp[2])
```

```{r}
set.seed(1)

weather_results = 
  weather_df %>% 
  select(tmin, tmax) %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    tidy_results = map(models, broom::tidy),
    glance_results = map(models, broom::glance)
  ) 

r_squares = weather_results %>% 
  select(glance_results) %>% 
  unnest(glance_results) %>% 
  select(r.squared) 

betas = weather_results %>% 
  select(tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(estimate) %>% 
  pull(1)

log_vals = numeric(length(betas)/2)

for (i in seq(1, length(betas), 2)) {
  #print(i)
  #print(log_vals[(i+1)%/%2])
  log_vals[(i+1)/2] = log(betas[i] * betas[i+1])
  #print(log(betas[i] * betas[i+1]))
  #print(log_vals[(i+1)/2])
  #break
}
```

R-squared distribution and 95% CI. The distribution is largely normal with a very slight left skew. Median is at 0.9118 with a 95% CI of (0.8937, 0.9271)
```{r}
r_squares %>% ggplot(aes(x = r.squared)) + geom_density()
summary(r_squares)
r_squares %>% pull(1) %>% quantile(c(.025, .975))
```

Log of B0 and B1 distribution and 95% CI. The distribution is largely normal with the median equal to the mean. Median (and mean) is at 2.013 with a 95% CI of (1.965, 2.059)
```{r}
log_vals = as_tibble(log_vals)
log_vals %>% ggplot(aes(x = value)) + geom_density()
summary(log_vals)
log_vals %>% pull(1) %>% quantile(c(.025, .975))
```

